GWAS_Prep

### 2019-08-29 Analysis/GWAS_Prep.Rmd
change alias2symbol

  #Summarise the results
  #Keeping track of changes (sapply necessary to keep placeholders for unmapped genes)
  recomb_genes = sapply(ebi_dat$MAPPED_GENE, function(x) alias2Symbol(x, species = "Hs"))
  recomb_genes = unlist(lapply(recomb_genes, function(x) paste0(x,collapse=' ')))
  change = (ebi_dat$MAPPED_GENE == recomb_genes)
  sum_vec = ifelse(change == TRUE, "Same", ifelse(change == FALSE & recomb_genes == "", "No Match", "Converted"))
  ebi_dat$MAPPED_GENE = recomb_genes
  return(ebi_dat)
}

>>>>

  #Summarise the results
  #Keeping track of changes (sapply necessary to keep placeholders for unmapped genes)
  recomb_genes = sapply(ebi_dat$MAPPED_GENE, function(x) alias2SymbolEbicat(x, species = "Hs"))
  recomb_genes = unlist(lapply(recomb_genes, function(x) paste0(x,collapse=' ')))
  change = (ebi_dat$MAPPED_GENE == recomb_genes)
  sum_vec = ifelse(change == TRUE, "Same", ifelse(change == FALSE & recomb_genes == "", "No Match", "Converted"))
  ebi_dat$MAPPED_GENE = recomb_genes
  return(ebi_dat)
}
